---
title: "SEP -- Assessment Data"
author: "Brief prepared by Joseph Diodato (jdiodato@iu.edu)"
date: "Fall 2019"
output:
  pdf_document: default
---

```{r, include = FALSE}
library(tidyverse)
```

# RPS Data Analysis Template
```{r, include = FALSE}
centers <- c("Ashton",'Briscoe', 'Collins', 'Eigenmann', 'Forest', 
             'Read', 'Spruce', 'Teter', 'USC', 'Wells', 'Willkie', 'Wright')
```

```{r, include = FALSE}
df <- data.frame("Center" = centers)
df$RA.Submissions <- NA
df$RA.Numbers <- NA
df$Staff.Submission.Rate <- NA
df$Number.Students <- NA
df$Percentage.Students <- NA
# Create more columns as needed.
```

```{r, include = FALSE}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```

```{r, include = FALSE}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)
```

## Overview

During the week of --/--/2019 (Residential Curiculum Week ---) Residential Staff facilitated SEP ---. Across campus -- Resident Assistants (%) submitted the SEP --- Wrap-up Form, tagging a total of -- residents (%)

**Include plot of staff submissions and RA tags ** 
The \texttt{markdown} package of [R/RStudio](https://www.r-project.org/about.html) as well as [Nvivo](https://www.qsrinternational.com/nvivo/nvivo-products) were used to prepare this brief.
## Results
## Conclusion
- Placeholder 1
- Placeholder 2
- Placeholder 3
